Placeholder Title... Something About Delegating Quantum Computations

### 2019-10-15 paper.tex
Write the ground state check
Fix underfull hbox
Do more work on longoutput
Use projection lemma
Make references clickable
Add TODOs from group discussion
Start typing ground state checking algorithm
Start lemma on intersecting kernels
Resolve TODOs on kernel intersections
Apply Chernoff's
Write first draft for amplification
Switch affiliation to NTU

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{braket}

\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

\author[1]{Kai-Min Chung}
\author[1]{Yi Lee}
\author[2]{Han-Hsuan Lin}
\author[3]{Xiaodi Wu}
\affil[1]{Institute of Information Science, Academia Sinica, Taipei, Taiwan}
\affil[2]{Department of Computer Science, University of Texas at Austin}
\affil[3]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}

\begin{document}

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{braket}
\usepackage{algorithm}
\usepackage{algpseudocode}
\newcommand{\sgn}{\operatorname{sgn}}
\DeclareMathOperator*{\E}{\mathbb{E}}
\DeclareMathOperator*{\spn}{\operatorname{span}}
\DeclareMathOperator*{\poly}{\operatorname{poly}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\usepackage{etoolbox}
\usepackage{hyperref}
\newcommand{\algorithmautorefname}{Algorithm}
\apptocmd{\thebibliography}{\raggedright}{}{}
\usepackage{cite,color,float}

\newcommand{\KM}[1]{{\footnotesize\color{cyan}[KM: #1]}}

\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{observation}[theorem]{Observation}

@@

\author[1]{Kai-Min Chung}
\author[2]{Yi Lee}
\author[3]{Han-Hsuan Lin}
\author[4]{Xiaodi Wu}
\affil[1]{Institute of Information Science, Academia Sinica, Taiwan}
\affil[2]{Department of Physics, National Taiwan University, Taiwan}
\affil[3]{Department of Computer Science, University of Texas at Austin, USA}
\affil[4]{
	Department of Computer Science, Institute for Advanced Computer Studies,
	and Joint Center for Quantum Information and Computer Science,
	University of Maryland, USA
}
\input{macros.tex}
\begin{document}
